---
title: "IBS intro to R"
author: "Shannon B. Hagerty"
date: "8/26/2019"
output:
  pdf_document: default
  html_document: default
---
## Incredibly Important Business Update 

**What is R**
- R is an open source programming language that is very popular for data analysis / data scien. 
- Its popularity means a lot of code is already written and available for you to do common data analysis tasks. 
```{r}
library(tidyverse)
library(ggthemes)
```
  
**Why should you learn R**
- It is open source 
- It enables you to create reproducible analyses, which can save you both time and some frustration
- It gives you a lot of great options for communicating your analyses out (i.e. ggplot for graphing,Rmarkdown for reports, shiny for apps)

**Introduction to Rstudio, Rmarkdown, and R**
- Rstudio is the IDE we like to use to write our R code
- Rmarkdown is a document that allows you to put code, graphs, and text in one document. 

#### Load Data
```{r}
forbes<-read_csv('Forbes2000.csv')
```
#### Explore the data set 
```{r}
glimpse(forbes)
```

#### Summarize the Data by category
```{r}
category_summary<- forbes %>% group_by(category) %>% summarize(mean_sales = mean(sales), mean_profit= mean(profits), mean_marketvalue = mean(marketvalue))
```
#### Plot the Summary
```{r}
ggplot(category_summary) + geom_bar(aes(x=category, y=mean_profit), stat="identity")+theme_economist()+coord_flip()+ylab('Average Profit')+xlab('')
```
Now I can tell you everything that is important about this graph in a really nice report. 

#### Can you make your own graph? 
Try to adjust the code below to summarize by the country column. 

**Summarize the Data by country**
```{r error=TRUE}
country_summary<- forbes %>% group_by(PUT_SOMETHING_HERE) %>% summarize(mean_sales = mean(sales), mean_profit= mean(profits), mean_marketvalue = mean(marketvalue))
```

Okay, now there are a lot of countries.  Take a look at the data set and lets select out only the countries with an average market value greater than 20.

**Get only countries with highest market value**
```{r error=TRUE}
country_summary<- country_summary %>% filter(mean_marketvalue > 20)
```

**ADAPT THE CODE BELOW TO Plot the country summary**
Try changing the metric we're plotting (i.e. instead of mean_marketvalue try mean_profit)
```{r error=TRUE}
ggplot(category_summary) + geom_bar(aes(x=category, y=mean_profit), stat="identity")+theme_economist()+coord_flip()+ylab('Average Profit')+xlab('')
```